---
title: "Package Tutorial"
author: "Amere Roussell"
date: "`r Sys.Date()`"
output: html_document
---

# An Introduction To My R Package

The purpose of this package is to make using data easier. It will allow the user to removed unwanted values, select columns, and plot information. Some times making plots and selecting data can be tedious, so this package is here to help. The point of these functions is to take out the middle step and allow the user to just put in the data and get their graphs.

## Download The Package

```{r}
remotes::install_github("Omnimere/Big.Job")
```

## Installation Instructions

```{r eval=FALSE, include=TRUE}
install.packages("phytools")
install.packages("tidyverse")
install.packages("ggplot")
```

To download the data use the code below.

```{r}
download.file(url="https://raw.githubusercontent.com/Omnimere/Roussell_pkg/master/Data/simulated_data_pps_data.csv", destfile = "/cloud/project/simulated_data_pps_data.csv")
```

The file will be saved as following.

```{r}
data <- read.csv("/cloud/project/simulated_data_pps_data.csv")
```
### Functions

If the data you are using is big or has columns that it specifically needed. This function will allow the you to select up to twelve of them. 

```{r}
Trial(data, column1, column2, column3, column4, column5, column6, column7, column8, column9, column10, column11, column12)
```

```{r}
Dataclean <- Trial(data, Theta, Tajima.D, Tajima.Pi, Segregating.Sites, Max.Pairwise.Difference, Max.Pairwise.Difference.Excluding.Ambiguous, Max.Variable.Block.Length, Max.Variable.Block.Length.Excluding.Ambiguous, Min.Pairwise.Difference, Min.Pairwise.Difference.Excluding.Ambiguous, Number.Invariable.Block.Excluding.Ambiguous)
```

Now we want to make sure that the data doesn't have any NA values.
```{r}
non(Dataclean)
```

Use this function for sectioning out columns to use in comparison to a mean.
```{r}
midmean(data, column1, column2, mean)
```
```{r}
midmean(Dataclean, Segregating.Sites, Tajima.Pi, Tajima.Pi)
```

###Now its time to make some graphs.

The first graph will be a line graph. This can be used to see relations with the two columns.
```{r}
Graph(data, column1, column2)
```
```{r}
Graph(Dataclean, Segregating.Sites, Tajima.Pi)
```

The next graph will be a histogram that shows the distribution of values in a selected column. 
```{r}
Histo(data, column)
```
```{r}
Histo(Dataclean, Segregating.Sites)
```

